Social Housing in Toronto

### 2024-04-22 paper/paper.qmd
commit

library(tidyverse)
library(palmerpenguins)

analysis_data <- read_csv(here::here("data/analysis_data.csv"))
```

@@

# Create a data frame
plot_data <- data.frame(
              quarter_year = year_quarter,
              test = total_active_waiting_list ,
              inactive_cancelled = inactive_cancelled
            )

>>>>

library(tidyverse)
library(palmerpenguins)
library(tinytex)

analysis_data <- read_csv(here::here("data/analysis_data.csv"))

@@

# Create a data frame
plot_data <- data.frame(
              quarter_year = year_quarter,
              test = test ,
              inactive_cancelled = inactive_cancelled
            )
